### 2017-11-10 monograph/thesis/chapters/good_practices.tex
Created the initial text for the section Test Drive Development on
monograph/thesis/chapters/good_practices.tex

    \cite{theImpactOfIdentifierStyle},
    \cite{womenAndMen},

@@

>>>>

    \cite{theImpactOfIdentifierStyle},
    \cite{womenAndMen},
    \url{https://en.wikipedia.org/wiki/Category:Naming_conventions}

@@

    \section{Test Drive Development}

    The only way to write Unit Test is by TDD.
    If you already had written the program,
    assure everything is under versioning control system and broke everything.
    Only then start writing Unit Tests by TDD,
    however you can cheat on how to write the new code.

    When did you finish writing the function/code? When cannot think/know how to write
    any test which will make you program fail.
    You my think,
    but if the function requirements are not finished yet? Then it means there are
    tests you can write which will make the function fail.
    Otherwise you already finished writing your tests.
